---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Developing Data Products - Week 3 Assignment

_Chandani Patel_

_08/04/2020_

# Introduction
This project is created as part of the Developing Data Products course of the Coursera Data Science Specialisation.

The goal of the project is to create a web page presentation using R Markdown that features a plot created with Plotly, and to host the resulting web page on either GitHub Pages, RPubs, or NeoCities.

The interactive plot on the next slide represents 

### Loading Libraries

```{r}
library(plotly)
```

### Load Data & Process Data
This step will load the data from csv and it will process it to agreegate the data by state and dates

```{r, echo=TRUE}
# Load Data sets
corona_data_us_counties <- read.csv("corona-data-us-counties.csv", header = TRUE)
state_codes <- read.csv("us_codes.csv", header = TRUE)
# Assign state code in main dataset from state_codes
corona_data_us_counties$code<-state_codes[match(corona_data_us_counties$state, state_codes$state),1]

# Agrregate data for day
datewise_data = aggregate(cases~state+date, data=corona_data_us_counties, FUN=sum)
deaths_flter_data = aggregate(deaths~state+date, data=corona_data_us_counties, FUN=sum)
datewise_data['deaths']=deaths_flter_data['deaths']

# Generate Data from states
statewise_data = aggregate(cases~state+code, data=corona_data_us_counties, FUN=sum)
deaths_satewise_data = aggregate(deaths~state, data=corona_data_us_counties, FUN=sum)
statewise_data['deaths'] = deaths_satewise_data['deaths']

```

### Plot the graph to show timeseris data of COVID-19

```{r, echo=TRUE}
fig <- datewise_data %>% plot_ly()
fig <- fig %>% add_trace(x = ~date, y = ~cases, type = 'bar', textposition = 'auto', name = 'Cases', 
                         marker = list(color = 'rgb(158,202,225)'))
fig <- fig %>% add_trace(x = ~date, y = ~deaths, type = 'bar', textposition = 'auto', name = 'Deaths',
                         marker = list(color = 'rgb(228,87,81)'))
fig <- fig %>% layout(title = list(text="US COVID-2019 Cases and Deaths Report", x=0),
                      barmode = 'group', xaxis = list(title = "Date"),
                      yaxis = list(title = "Cases V/S Deaths"))
fig
```

### Plot the map graph to show state wise data of COVID-19
```{r, echo=TRUE}
statewise_data$hover <- with(statewise_data, paste(state, '<br>', "Cases", cases, "Deaths", deaths))
# give state boundaries a white border
l <- list(color = toRGB("red"), width = 2)
# specify some map projection/options
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('red')
)

mapfig <- plot_geo(statewise_data, locationmode = 'USA-states')
mapfig <- mapfig %>% add_trace(
  z = ~cases, text = ~hover, locations = ~code,
  color = ~cases, colors = 'Reds'
)
mapfig <- mapfig %>% colorbar(title = "Cases")
mapfig <- mapfig %>% layout(
  title = list(text='COVID-19 cases v/s deaths in US <br>(Hover for breakdown)', x = 0.2),
  geo = g
)
mapfig
```