---
date: "08/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Coursera R Markdown and Leaflet
_Chandani Patel_

_08-April-2020_

## Instructions
Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

## Submission

## Load libraries & Create Map
Create a leaflet map object.
```{r cars}
library(leaflet)
map <- leaflet() %>% addTiles()
```

## Create the marker

```{r}
efilTowerIcon <- makeIcon(
   iconUrl = "https://static-s.aa-cdn.net/img/gp/20600003662901/gpCpv7lIvX6jVQUR2Nn1cfaq7aU3T5HTAVa75C39H53XrL4uGVVATjqOlTILm_AyCA=w300?v=1",
   iconWidth = 256, iconHeight = 30,
   iconAnchorX = 256, iconAnchorY = 30)
```

### Plot created marker on map
```{r}
efilTowerPopup <- c("<a href= 'https://en.wikipedia.org/wiki/Eiffel_Tower' >Efil Tower<br><img src='https://static-s.aa-cdn.net/img/gp/20600003662901/gpCpv7lIvX6jVQUR2Nn1cfaq7aU3T5HTAVa75C39H53XrL4uGVVATjqOlTILm_AyCA=w300?v=1' width='200' height='200'  alt='Eiffel Tower' title='Eiffel Tower'></a>")
map %>%
   addTiles() %>%
   addMarkers(lat=48.8584, lng=2.2945, popup = efilTowerPopup)
```

## Ploting Markers
```{r}
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=18.9775, lng=72.8064, popup="Shree Mahalakshmi Temple, Bombay") %>%
  addMarkers(lat=18.9322,lng=72.8264, popup="Churchgate, Bombay") %>%
  addMarkers(lat=18.7557,lng=73.4091, popup="Lonavla, Maharashtra") %>%
  addMarkers(lat=18.9220,lng=72.8347, popup="Gateway of India, Mumbai") %>%
  addMarkers(lat=19.0168,lng=72.8302, popup="Siddhivinayak Temple, Mumbai") #%>%
m  # Print the map
```

# Mapping Clusters

```{r}
df <- data.frame(lat=runif(500, min=22.30, max = 33.93 ),
                 lng=runif(500, min=72.13, max = 77.15 ))
df %>%
leaflet() %>%
addTiles() %>%  
addMarkers(clusterOptions = markerClusterOptions())  
```